### 2020-04-14 system-model.tex
:pencil: Simplify target function

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \text{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
	\end{subsection}

@@

		where $k_i=i_s/i!(nv_t)^i$. We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on power transfer. Note that $\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}^3(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}^3(t)\}\}=0$, $\mathcal{E}\{\mathcal{A}\{y_{I,k}^2(t)y_{P,k}^2(t)\}\}=\mathcal{A}\{\mathcal{E}\{y_{I,k}^2(t)\}\}\mathcal{A}\{y_{P,k}^2(t)\}$, and the remaining terms are expressed by \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}. Since $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, modulation provides a power gain to the nonlinear terms in the output DC current.

@@

				 & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                                              \\

@@

				 & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})}                         \\

@@

				 & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                                             \\

@@

				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\label{eq:A{y_{P,k}**4'}}

@@

					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})

>>>>

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \text{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
	\end{subsection}

@@

		where $k_i=i_s/i!(nv_t)^i$. We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on power transfer. Note that $\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}^3(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}^3(t)\}\}=0$, $\mathcal{E}\{\mathcal{A}\{y_{I,k}^2(t)y_{P,k}^2(t)\}\}=\mathcal{A}\{\mathcal{E}\{y_{I,k}^2(t)\}\}\mathcal{A}\{y_{P,k}^2(t)\}$, and the remaining terms are expressed by \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}. It is noteworthy that modulation provides a power gain to the nonlinear terms in the output DC current as $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$.

@@

				%  & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                      \\
				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                         \\

@@

				%  & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})} \\
				 & =\frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})} \\

@@

				%  & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                     \\
				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                         \\

@@

				%  & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}  \\
				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}
				\label{eq:A{y_{P,k}**4'}}

@@

					% &=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
					% &\quad+\frac{3}{2}{k_4'}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})\\
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
